%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume
\documentclass[margin,line]{resume}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Abhishek Gupta}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    IIIrd Year Undergraduate Student \hfill mobile: +91 9958 003 242 \vspace{0mm}\\\vspace{0mm}%
    Indian Institute of Technology Delhi \hfill webpage: www.cse.iitd.ernet.in/~cs1090174 \vspace{0mm}\\\vspace{0mm}%
    New Delhi, India \hfill e-mail: cs1090174@cse.iitd.ernet.in  \vspace{0mm}\\\vspace{-4.5mm}%


    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}

    Virtualization, Cloud Computing, Machine Learning and its applications.

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{Indian Institute of Technology} Delhi, India \vspace{2mm}\\\vspace{1mm}%
    \textsl{B.Tech in Computer Science and Engineering} \hfill \textbf{ July 2009 -- present}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Expected graduation date: August 2013
        \item References: Prof. Subhashis Banarjee and Prof. Manik Verma  
    \end{list2}\vspace{-1.5mm}

    %__________________________________________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honours and\\Awards} 
    Summer Undergraduate Research Award 2011 for project on Cloud computing and Virtualization \vspace{1mm}\\%
    Kishore Vaigyanik Protsahana Yojna 2009 scholarship for students interested in Research\vspace{1mm}\\%
    First prize in Yahoo Hack U, Northern Region, India\vspace{1mm}\\%
    National Talent Search Examination (NTSE-2007) scholarship\vspace{1mm}\\%
    Felicitated by Chief Minister of the State for excellent performance in IIT JEE 2009 \vspace{1mm}\\%
    CBSE merit certificate for being among the top 0.1\% students by CBSE in Mathematics, 2007
    %__________________________________________________________________________________________________________________
    % Publications
    \section{\mysidestyle Selected Publications}

\vspace{-2mm}
    Abhishek Gupta, Daniel J. Mathew, Huzur Saran, Jatin Kumar, Sorav Bansal, Subhashish Banarjee, ``Design and Implementation of the Workflow of an Academic Cloud'',
    In \textsl{Springer Publications}, volume LNCS 7108, pp. 16-27, 2011.

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    \textbf{Indian Institute of Technology} Delhi, India\vspace{1mm}\\\vspace{1mm}%
    \textsl{System Administrator} \hfill \textbf{December 2010 -- present}\\
    Currently serving as the voluntary system adminstrator of the Computer Science and Engineering Department. Maintain over 100 clients, 25 servers and around 15 IT services, like authentication, mailing, directory service, internet access, course management, remote client management, etc.

    %__________________________________________________________________________________________________________________
    % Projects
    \section{\mysidestyle Projects}

    \textbf{Dynamic Rich Visual Interactive Narratives}   \hfill(Prof. Manik Verma)\vspace{1mm}\\\vspace{1mm}%
    \textsl{Information Retrieval}                        \hfill(July 2011 -- present)
    \begin{list2}
        \item Develop dynamic visual narratives timelines based on text in wikipedia
        \item Develop heuristics so as to improve the overall user experience and the relevancy of the images
    \end{list2}

    \textbf{Intelligent Notice Board}                           \hfill(Prof. M Balakrishnan)\vspace{1mm}\\\vspace{1mm}%
    \textsl{Embedded Systems}                                   \hfill(Oct, 2010 - Feb, 2011)
    \begin{list2}
        \item Campus based electronic notice board, driven by a Texas Instrument's DaVinci Multimedia Board
        \item Developed a web server and a client application on ARM board to make system schedule notices and posters
    \end{list2}

    \textbf{Baadal – An orchestrator}                           \hfill(Prof. Sorav Bansal and Prof. Subhashish Banarjee)\vspace{1mm}\\\vspace{1mm}%
    \textsl{Virtualization and cloud computing}                 \hfill(May, 2011 - Aug, 2011)
    \begin{list2}
        \item Intra campus Cloud computing facility similar to Amazon EC2 for facilitating scientific and research related
heavy computation
        \item Analyzing overall performances, setting benchmarks and comparing the performances with the other more
readily available systems like Xen and VMWare
        \item Writing a suitable API to administer the virtual machines, which was used to develop commandline and a web
interface for the same
    \end{list2}

    \textbf{Optimizing Season vertical for Bing Image search}   \hfill(Prof. Manik Verma)\vspace{1mm}\\\vspace{1mm}%
    \textsl{Web Search and Machine Learning}                    \hfill(July 2011 -- present)
    \begin{list2}
        \item Develop the training data set for over 50 cities and four seasons
        \item Developed heruistics for building a re-ranker to optimize the current search for the subset of queries
    \end{list2}
        
    \textbf{Rationality in Decision Making}                     \hfill(Dr. Purnima Singh)\vspace{1mm}\\\vspace{1mm}%
    \textsl{Social Psychology}                                  \hfill(July, 2011 - Present)
    To explore whether human beings are rational in their approach of making decisions and how the rationality is       influenced by social factors like their ambitions and moral values.
    
    \textbf{Course Projects}
    \begin{list2}
        \item Multiplayer Ping Pong Game (Networking) (July, 2010 - Nov, 2010) : Multiplayer networking game supporting
upto four players. Game was coded in C++ using OpenGL. Only submission which used UDP broadcasting for the
clients to automatically search for the available servers
         \item MIPS-32 Processor Design (Computer Architecture) (July, 2010 - Nov, 2010) : Designed a subset of MIPS-32
instruction set on a simulator. The application computes and displays the day of the week corresponding to the
specified date
        \item Implementation of Systolic Sorting Architecture on FPGA Board (Embedded Systems) (Jan, 2011 - Apr,
2011) : Implemented sorting of numbers on FPGA board via the systolic array of Digital Processing Units (DPUs).
Code was written in VHDL.
        \item Android Application for GPS Navigation (July, 2010 - Nov, 2010) : An android application in Java and Web
interface in PHP, Javascript, Jquery and Ajax for finding the shortest path from one point to another based on
current traffic density.
        \item Interpreters for subsets of Prolog and SML (Programming Languages) (Jan, 2011 - Apr, 2011) : Built a
lexer, parser and an interpreter for a subset of the functions provided by SML and prolog.
    \end{list2}
    
    %__________________________________________________________________________________________________________________
    % Scholastic Achievements
    \section{\mysidestyle Scholastic\\Achievements} 
    Among the top 300 students who qualied for :\vspace{1mm}\\\vspace{-4mm}
    \begin{list2}
	\item Indian National Physics Olympiad (INPhO) 2008-09
	\item Indian National Chemistry Olympiad (INChO) 2008-09
	\item Regional Mathematics Olympiad (RMO) 2007-2008
    \end{list2}\vspace{-1.5mm}
    All India Rank 3 in National Science Talent Search Examination (NSTSE-2009)\vspace{1mm}\\%
    All India Rank 6 in National Science Olympiad (NSO-2008)\vspace{1mm}\\%
    All India Rank 139 in IIT JEE and 78 in AIEEE 2009

    %__________________________________________________________________________________________________________________
    % Other Activities
    \section{\mysidestyle Other\\Activities}
    Attended the summer camp on Information Retrieval and Web Search by Yahoo in Bangalore\vspace{1mm}\\%
    Presented poster in the Openhouse 2011, IIT Delhi and Information Knowledge Exchange Symposium, ACM, IIT Delhi. Won the first prize in IKES 2011\vspace{1mm}\\%
    Second Prize in Algorithms, Tryst 2011 and Helix (game programming), Tryst 2010 the annual\\%
    technical festival of IIT Delhi\vspace{1mm}\\%
    Activity head of Website Team, Tryst 2010 and Online Treasure hunt (Krypton), Tryst 2011

    %__________________________________________________________________________________________________________________
    % Positions of Responsibility
    \section{\mysidestyle Position of \\Responsibilities}
    \textbf{Indian Institute of Technology} Delhi, India\vspace{2mm}\\\vspace{1mm}%
    \textsl{Vice Chairman, ACM chapter} \hfill \textbf{July 2011 -- present}\\
    Currently serving as the Vice Chairman of ACM Chapter of IIT Delhi which was preceeded by a role of Technical Associate from July 2010 to July 2011.\vspace{2mm}\\\vspace{1mm}%
    \textsl{Student Mentor} \hfill \textbf{July 2011 -- present}\\
    Currently serving as a Student Mentor for the CSE Department First Year Students. Helped them get acquainted with the college studies and environment.

    \textsl{National Service Scheme Executive} \hfill \textbf{April 2010 -- April 2011}\vspace{1mm}\\%
    \begin{list2}
	\item Worked on an online database of blood donors to manage effectively and track the blood donations
	\item Created facebook applications for social impact and build up the NSS Website
    \end{list2}\vspace{-1.5mm}

    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Programming} 
    Python, Linux Shell Programming, Java, C/C++, C\#, SML, PHP, Prolog, Javascript, Octave, \LaTeXe, SQL

    \section{\mysidestyle Softwares} 
    Xilinx, Eclipse, Visual Studio, Web2py, Drupal, Wordpress


    %__________________________________________________________________________________________________________________
    % Referees
    %______________________________________________________________________________________________________________________
    \section{\mysidestyle Referees}
    %{\sl Available on request.}
    \begin{tabular}{@{}p{4cm}p{5.5cm}p{5cm}}
    \textbf{Prof. Manik Verma}       	&  \textbf{Prof. Subhashis Banarjee} 	&  \textbf{Prof. Sorav Bansal}          \\
    Researcher                          &  Professor                       	&	Professor			\\
    Microsoft Research                	&  Indian Institute of Technoglogy      & Indian Institute of Technology	\\
    Bangalore, India          		&  New Delhi, India        		& New Delhi, India			\\
    \end{tabular}

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF